One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change

### 2020-02-25 article4_jbr_diss.rnw
submitted dissertation

\begin{frontmatter}
%Lock, Stock and Two Smoking Barrels lock stock and two mediating factors
%The Lord of the Rings: The Two Towers
%Bravo Two Zero (1999)
%A tale of two mechanisms
%Eating strategy for breakfast?
%Push, skill and two mediating factors

\title{One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

\begin{abstract}
% This paper investigates strategic cognition as mediating factor in the dynamic
% capabilities-competitive advantage relationship. By including strategic cognition into the
% analysis in addition to the conventional mediator (operating capabilities) we argue that a
% more holistic approach to understanding the workings of dynamic capabilities emerges. We
% introduce two expressions of how dynamic capabilities work, namely as a conductor (the
% conventional mechanism) and as a coach (the cognitive mechanism). Using repeated
% cross-sectional data from Norwegian technology firms our results indicate support for our
% holistic model. This has implications for understanding how dynamic capabilites work, as
% well as practical implications for how strategic change is implemented in firms.

  The ultimate goal in the theory of dynamic capabilities (DCs) is competitive advantage.
  This paper analyzes to what extent DCs influence competitive advantage through two paths
  - one old, and one new - namely behavioral and non-behavioral objects of change.  In
  addition to emergent theorizing and real world examples, we use the metaphor of “DC as
  coach” and DC as conductor” to build a conceptual model and derive hypotheses.  Using
  longitudinal survey data with a 10 year time lag we find that DCs influence competitive
  advantage through both paths. Thus, the paper empirically validates emergent theorizing
  proposing non-behavioral objects of change as a new path between DC and competitive
  advantage. Moreover, the paper helps to broaden the conceptual basis for empirically
  investigating how DCs enable competitive advantage. This has implications for
  understanding how dynamic capabilities work, as well as practical implications for how
  strategic change is implemented in firms.

\end{abstract}

@@

\end{frontmatter}

@@

\doublespacing

@@

<<loading, results="asis", echo=FALSE >>=
setwd("/Users/larshovdanmolden/Documents/git/article4")
library(xtable)
library(semPLS)
load("./data/resart4.RData")
r <- main$resmat
rm  <- main$resmatmed
l  <- main$loadings
ic <- data.frame(i[,c(1,4)]);colnames(ic) <- c("b","t")
ic$rn  <- 1:nrow(ic)
bb <- main$models$both
bm <- main$models$mmed
br <- main$models$rmed
#foolars=0.99
@

@@

\begin{align}
  CA_{i,1} & = \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i \\
  CAP_{i,1} & = \beta_0 + \beta_1 CAP_{i,0} + \beta_2 DC_{i,0} + v_i\\
   COG_{i,1} & = \eta_0 + \eta_1 COG_{i,0} + \eta_2 DC_{i,0} +  u_i
\end{align}

@@

\begin{table}[t]
  \caption{PLS-SEM results for key constructs}
\label{tab:res}
  \scriptsize
  <<child-demo, child='/Users/larshovdanmolden/Documents/git/article4/figure/restab.rnw'>>=
@
   \begin{tablenotes}
      \tiny
      \item Standard-errors estimated using bootstrapping with 10 000 simulations.
      \item Firm level control variables include firm size, firm age,
        profit margin, firm assets.
    \end{tablenotes}
  \end{table}

@@

 <<pathchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/medanalysisall.rnw',results="asis">>=
@

@@

\section*{Bibliography}

\singlespacing
\bibliography{Dissertation_clean}

\section*{Appendix}
\newpage

  \begin{table}\label{tab:items}
    \caption{Core constructs and their measurement items. Factor
      loadings in parantheses}
    <<itemchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/itemtab.rnw',results="asis">>=
    @
    \begin{tablenotes}
      \tiny
      \item Dillon-Goldstein Rho is recommended as reliability measure
        for SEM-PLS \citep{Hair2019}.
    \end{tablenotes}
  \end{table}

>>>>

%\begin{frontmatter}
%Lock, Stock and Two Smoking Barrels lock stock and two mediating factors
%The Lord of the Rings: The Two Towers
%Bravo Two Zero (1999)
%A tale of two mechanisms
%Eating strategy for breakfast?
%Push, skill and two mediating factors

%\title{One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

% This paper investigates strategic cognition as mediating factor in the dynamic
% capabilities-competitive advantage relationship. By including strategic cognition into the
% analysis in addition to the conventional mediator (operating capabilities) we argue that a
% more holistic approach to understanding the workings of dynamic capabilities emerges. We
% introduce two expressions of how dynamic capabilities work, namely as a conductor (the
% conventional mechanism) and as a coach (the cognitive mechanism). Using repeated
% cross-sectional data from Norwegian technology firms our results indicate support for our
% holistic model. This has implications for understanding how dynamic capabilites work, as
% well as practical implications for how strategic change is implemented in firms.

{\large \bf One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change}\\
\newline

% \begin{abstract}
{\bf Abstract:}\\
  The ultimate goal in the theory of dynamic capabilities (DCs) is competitive advantage.
  This paper analyzes to what extent DCs influence competitive advantage through two paths
  - one old, and one new - namely behavioral and non-behavioral objects of change.  In
  addition to emergent theorizing and real world examples, we use the metaphor of “DC as
  coach” and DC as conductor” to build a conceptual model and derive hypotheses.  Using
  longitudinal survey data with a 10 year time lag we find that DCs influence competitive
  advantage through both paths. Thus, the paper empirically validates emergent theorizing
  proposing non-behavioral objects of change as a new path between DC and competitive
  advantage. Moreover, the paper helps to broaden the conceptual basis for empirically
  investigating how DCs enable competitive advantage. This has implications for
  understanding how dynamic capabilities work, as well as practical implications for how
  strategic change is implemented in firms.

%\end{abstract}

@@

%\end{frontmatter}

@@

%\doublespacing

@@

%Frame flexibility: The role of cognitive and emotional framing in innovation adoption by incumbent firms rafaelli2019

<<loading, results="asis", echo=FALSE >>=
setwd("/Users/larshovdanmolden/Documents/git/article4")
#library(xtable)
#library(semPLS)
#load("./data/resart4.RData")
r <- main$resmat
rm  <- main$resmatmed
l  <- main$loadings
ic <- data.frame(i[,c(1,4)]);colnames(ic) <- c("b","t")
ic$rn  <- 1:nrow(ic)
bb <- main$models$both
bm <- main$models$mmed
br <- main$models$rmed
#foolars=0.99
@

@@

\begin{align}
  CA_{i,1}  = & \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1} + \\
           & \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i
\end{align}

\begin{align}
  CAP_{i,1} & = \beta_0 + \beta_1 CAP_{i,0} + \beta_2 DC_{i,0} + v_i\\
   COG_{i,1} & = \eta_0 + \eta_1 COG_{i,0} + \eta_2 DC_{i,0} +  u_i
\end{align}

@@

\begin{table}[t]
  \caption{PLS-SEM results for key constructs}
\label{tab:res}
  \scriptsize
  <<child-demo, child='/Users/larshovdanmolden/Documents/git/article4/figure/restab.rnw'>>=
@
\begin{tablenotes}

      \tiny
      \item Standard-errors estimated using bootstrapping with 10 000 simulations. \vspace{-1em}
      \item Firm level control variables include firm size, firm age,
        profit margin, firm assets.
    \end{tablenotes}
  \end{table}

@@

\begin{figure}\label{fig:med4}
 <<pathchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/medanalysisall.rnw',results="asis">>=
@
\caption{Mediation analysis - graphical representation}
\end{figure}

@@

%\section*{Bibliography}

%\singlespacing
%\bibliography{Dissertation_clean}

\section*{Appendix}

\begin{table}[t!]
  \label{tab:items}
    \caption{Core constructs and their measurement items. Factor
      loadings in parantheses}
    <<itemchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/itemtab.rnw',results="asis">>=
    @
    \begin{tablenotes}
      \tiny
      \item Dillon-Goldstein Rho is recommended as reliability measure
        for SEM-PLS \citep{Hair2019}.
    \end{tablenotes}
  \end{table}
